\Chapter{Preface}

%%%%%%%%%%%%%%%%%%%%%%%%%
\Section{Disclaimer}

*This is not an official release yet*, this is a version in development. 
This particular version, 0.0.1, changes from one day to another without warning 
and even without a change in the version number. Also, the operations and 
global variables can still change name or even disappear without warning. 
No commitment is made at the moment concerning compatibility of this version of 
the software with any future version.

As of this writing (14/Feb/2016) there are only two trustable chapters in this manual: 
`YAGS Functions by Topic' and  `YAGS Functions Reference'; also the file 
`cheatsheet-yags.pdf' (within directory: `<YAGSDIR>/doc/') may be useful. 
All other chapters may contain errors, broken links and misleading information (with higher probability).

The first official version will be 0.0.2 and is scheduled to be ready this year (2016), 
so come back soon.


%%%%%%%%%%%%%%%%%%%%%%%%%
\Section{Welcome to YAGS}

{\YAGS} - <Yet Another Graph System> is a computing system for dealing with graphs, in the sense of Graph Theory (not bar graphs, pie charts nor graphs of functions). Hence our graphs are ordered pairs $G=(V,E)$, where 
$V$ is a finite set of vertices and $E$ is a finite set of edges which are (ordered or unordered) pairs of vertices.

{\YAGS} was initiated by M.A. Piza{\~n}a in May 2003, and soon incorporated the work of R. MacKinney-Romero and R. Villarroel-Flores.

Our motivation here was this and that.

Our Pourposes and Aim.

authors, contacts


%%%%%%%%%%%%%%%%%%%%%%%%%
\Section{Citing YAGS}

If you publish a result and you used {\YAGS} during your research, please cite us as you would normally do with a research paper:

R. MacKinney-Romero, M.A. Piza{\~n}a and R. Villarroel-Flores.\newline
<YAGS - Yet Another Graph System, Version 0.0.1> (2016)\newline
http://xamanek.izt.uam.mx/yags/

\begintt
@manual{YAGS,
author = {R. MacKinney-Romero and M.A. Piza{\~n}a and R. Villarroel-Flores},
 title = {YAGS - Yet Another Graph System, Version 0.0.1},
  year = {2016},
  note = {http://xamanek.izt.uam.mx/yags/},
}
\endtt

%%%%%%%%%%%%%%%%%%%%%%%%%
\Section {Copyright}

{\YAGS} - Yet Another Graph System\newline
Copyright (C) 2016  R. MacKinney-Romero, M.A. Piza{\~n}a and R. Villarroel-Flores.

This program is free software: you can redistribute it and/or modify
it under the terms of the GNU General Public License as published by
the Free Software Foundation, either version 3 of the License, or
(at your option) any later version.

This program is distributed in the hope that it will be useful,
but WITHOUT ANY WARRANTY; without even the implied warranty of
MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
GNU General Public License for more details.

For details, see the file GPL in the installation directory of {\YAGS} typically 
under `GAP-Dir/pkg/yags/GPL' or see `http://www.gnu.org/licenses/gpl-3.0.html'.

`yags@xamanek.izt.uam.mx'\newline
`http://xamanek.izt.uam.mx/yags/'\newline
`https://github.com/yags/main/'

%%%%%%%%%%%%%%%%%%%%%%%%%
\Section{Authors}

The authors of {\YAGS} in the chronological order of their first contribution are as follows:

M.A. Piza{\~n}a\newline
Departamento de Ingenier\'{\i}a El\'{e}ctrica\newline
Universidad Aut\'{o}noma Metropolitana\newline
\Mailto{map@xanum.uam.mx}

R. MacKinney-Romero\newline
Departamento de Ingenier\'{\i}a El\'{e}ctrica\newline
Universidad Aut\'{o}noma Metropolitana\newline
\Mailto{rene@xanum.uam.mx}

R. Villarroel-Flores\newline
Centro de Investigaci\'{o}n en Matem\'{a}ticas\newline
Universidad Aut\'{o}noma del Estado de Hidalgo\newline
\Mailto{rafaelv@uaeh.edu.mx}

%%%%%%%%%%%%%%%%%%%%%%%%%
\Section{More Information}

More information about {\YAGS} can be found on its official web page:

`http://xamanek.izt.uam.mx/yags/'

You can receive notifications about {\YAGS} (i.e. new releases, bug fixes, etc.) by subscribing to its email distribution list:

`http://xamanek.izt.uam.mx/cgi-bin/mailman/listinfo/yagsnews/'

If you are a developer, you may contribute to our project on public repository:

`https://github.com/yags/main/'


